|

### 2025-05-24 doc/paper.qmd
Makefile configuration

The assumptions guiding the comparison are as follows: visual inspection is used to assess trends in life expectancy and income per capita; bubble size reflects each country’s population, as defined by Gapminder; and no new calculations are applied - the 2021 snapshot displays curated values from the Gapminder Foundation [-@gapminder_health_chart].

>>>>

The assumptions guiding the comparison are as follows: visual inspection is used to assess trends in life expectancy and income per capita; bubble size reflects each country’s population, as defined by Gapminder; no new calculations are applied - the 2021 snapshot displays curated values from the Gapminder Foundation [-@gapminder_health_chart].
